### 2016-10-11 Manuscript/SW_early_life_telomeres.Rmd
Edits

2. We tested how spatiotemporal in longitudinal telomere dynamics are related to ecology and survival in the Seychelles warbler (*Acrocephalus sechellensis*), using a large dataset of `r nrow(dd)` samples from multiple cohorts spanning `r max(juv$LayYear)-min(juv$LayYear)` years.

@@

>>>>

2. We provide a detailed analysis of how telomere dynamics vary over individual lifespans, and with spatiotemporal variation in the social and ecological environment, in the Seychelles warbler (*Acrocephalus sechellensis*). We use one of the largest longitudinal datasets to date, consisting of `r nrow(dd)` samples from multiple cohorts spanning `r max(juv$LayYear)-min(juv$LayYear)` years.

@@

head(dd3)
fit <- coxph(Surv(RemainingLife, RemainingLife1, Died1) ~ Agemonths1 + RTL1,
              data=dd3)

 dd3 <- subset(dd3,RemainingLife-RemainingLife1 >0)

which(is.na(dd3$RemainingLife1))
which(is.na(dd3$RTL1))
